Supporting Information : Asymmetric tail-association in extreme climatic events affects population-extinction risk

### 2019-10-12 SuppMat.Rmd
rearranging figs...continued

```{r fig_agestr_mtd_linear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: moderate LTdep.,C","vital rates: moderate RTdep.,SC"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2, seg.len = 1)
par(op)
dev.off()
```

@@

```{r fig_agestr_mtd_nonlinear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: moderate LTdep.,C","vital rates: moderate RTdep.,SC"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2, seg.len = 1)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: extreme LTdep.","vital rates: extreme RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf
xR<-nlas_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("vital rates: extreme LTdep.","vital rates: extreme RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5, x.intersp = 0.2)
par(op)
dev.off()
```

@@

pdf("./Results/common_legend_extreme_and_moderate_noise.pdf",height=1,width=12)
op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("center", c("extreme LT","moderate LT", "moderate RT","extreme RT"), lty=c(1,1), pch=c(1,1,1,1), 
         col=c('red', 'orange','skyblue','blue'),x.intersp = 0.1,
         cex = 2.2, xpd = TRUE, horiz = T, inset = c(0,0), 
         bty = "n")
par(op)
dev.off()

@@

#-------------------------------------- plot for moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_ext_risk_local_disp_moderatenoise.pdf",sep=""),height=9,width=9)

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#----------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"hassell_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#---------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"msmith_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5))

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"msmith_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#--------------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"pennycuick_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.2,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"pennycuick_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#------------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"verhulst_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"verhulst_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#--------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"abrewer_ext_risk_local_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_mleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"abrewer_ext_risk_global_disp_extreme_and_moderatenoise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"abrewer_extrisk_d0_extreme_and_moderatenoise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#------------- for extreme and moderate tail dep. noise : local dispersal summary fig. ---------------------
pdf("./Results/allmodel_ext_risk_local_disp_extreme_and_moderate_noise.pdf",height=12,width=9)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend("topleft", c("extreme LT","moderate LT","moderate RT","extreme RT"), lty=c(1,1,1,1), pch=c(1,1,1.1), 
       col=c('red', 'orange','skyblue','blue'), horiz=F, bty='o', cex=1.5, adj=0, x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-9, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-11, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist,noisetype = "both")

@@

pdf("./Results/allmodel_ext_risk_global_disp_extreme_and_moderatenoise.pdf",height=12,width=9)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend("topleft", c("extreme LT","moderate LT","moderate RT","extreme RT"), lty=c(1,1,1,1), pch=c(1,1,1.1), 
       col=c('red', 'orange','skyblue','blue'), horiz=F, bty='o', cex=1.5, adj=0, x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-9, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-11, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist, noisetype = "both")

@@

<!--FIG:  age structure model results for moderate tail dep. (C, SC)-->
\begin{figure}[!h]
\begin{center}
\textbf{ \hspace{0.5 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_100.pdf}
\caption[Extinction risk from single patch age structured models with time when vital rates have either left (C) or right tail (SC) association.]{Extinction risk (shading represents 95\% confidence interval) from single patch age structured models with time for 10000 simulations. Fecundity of adults and survival of eggs have moderate tail association in either left or right tail in their corresponding copula structure. Moderate left tail association (or right tail association) was generated by a bivariate Clayton (or Survival Clayton) copula with Kendall correlation coefficient = 0.6, $(A)$ for linear model ($\Omega = \infty$) and for $(B)$ non-linear model ($\Omega = 100$).\label{fig_extrisk_agestr_mtd}}
\end{center}
\end{figure}

<!--FIG:  summary: all nonlinear model results for local dispersion, moderate noise : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_local_disp_moderatenoise.pdf}
\caption[Analogous figure as that of Fig. \ref{MT-fig_extrisk_allmodel_localdisp_etd} in the maintext but with moderate tail association in spatially correlated noises.]{Analogous figure as that of Fig. \ref{MT-fig_extrisk_allmodel_localdisp_etd} in the maintext but with moderate tail association in spatially correlated noises.\label{fig_extrisk_allmodel_localdisp_mtd}}
\end{center}
\end{figure}

<!--FIG:  summary: all nonlinear model results for global dispersion, extreme noise : extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extremenoise.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{For each of six nonlinear density-dependence models presented in Table \ref{MT-tab_model_summary} with global dispersal, extinction risk varies as dispersion-rate ($d$) goes from $0$ to $0.5$. Last two columns represent extinction risk calculated for bifurcation parameter $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog, respectively.\label{fig_extrisk_allmodel_globaldisp_etd}}
\end{center}
\end{figure}

>>>>

```{r fig_agestr_mtd_linear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("moderate LT","moderate RT", expression(paste(Omega,"= ", infinity))), lty=c(1,1, NA),  
       col=c('red', 'blue', NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       )
par(op)
dev.off()
```

@@

```{r fig_agestr_mtd_nonlinear, echo=F,results="hide"}
xL<-C_age$extdf
xR<-SC_age$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("moderate LT","moderate RT", as.expression(bquote(Omega==.(omg)))), lty=c(1,1,NA),  
       col=c('red', 'blue',NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       )
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf
xR<-las_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("extreme LT","extreme RT", expression(paste(Omega,"= ", infinity))), lty=c(1,1, NA),  
       col=c('red', 'blue', NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       )
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf
xR<-nlas_exR$extdf
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend(x=-2,y=1.05, c("extreme LT","extreme RT", as.expression(bquote(Omega==.(omg)))), lty=c(1,1,NA),  
       col=c('red', 'blue',NA), horiz=F, bty='n', cex=1.5, x.intersp = 0.2
       #, seg.len = 1
       )
par(op)
dev.off()
```

@@

pdf("./Results/common_legend_extreme_and_moderate_noise.pdf",height=1,width=12)
op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("center", c("extreme LT,","moderate LT,", "moderate RT,","extreme RT"), lty=c(1,1), pch=c(1,1,1,1), 
         col=c('red', 'orange','skyblue','blue'),x.intersp = 0.1,
         cex = 2.2, xpd = TRUE, horiz = T, inset = c(0,0), 
         bty = "n")
par(op)
dev.off()

@@

#-------------------------------------- plot for moderate tail dep. noise --------------------------------------
pdf(paste(resloc,"ricker_ext_risk_local_disp_moderatenoise.pdf",sep=""),height=9,width=9)

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"ricker_extrisk_d0_extreme_and_moderate_noise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#----------------------- plot for extreme and moderate tail dep. noise --------------------------------------
pdf(paste(resloc,"hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"hassell_extrisk_d0_extreme_and_moderate_noise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#---------------------- plot for extreme and moderate tail dep. noise --------------------------------------
pdf(paste(resloc,"msmith_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"msmith_extrisk_d0_extreme_and_moderate_noise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#--------------------------- plot for extreme and moderate tail dep. noise --------------------------------------
pdf(paste(resloc,"pennycuick_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.2,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp_extreme_and_moderate_noise.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"pennycuick_extrisk_d0_extreme_and_moderate_noise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#------------------------- plot for extreme and moderate tail dep. noise --------------------------------------
pdf(paste(resloc,"verhulst_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp_extreme_and_moderate_noise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"verhulst_extrisk_d0_extreme_and_moderate_noise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#--------------------- plot for extreme and moderate tail dep. noise --------------------------------------
pdf(paste(resloc,"abrewer_ext_risk_local_disp_extreme_and_moderate_noise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(ss$d,ss$risk_xleft,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_mleft,type="b",col="orange")
  lines(ss$d,ss$risk_mright,type="b",col="skyblue")
  lines(ss$d,ss$risk_xright,type="b",col="blue")
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"abrewer_ext_risk_global_disp_extreme_and_moderate_noise.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

#-------------------- plot for extreme and moderate tail dep. noise ---------------------------------------
pdf(paste(resloc,"abrewer_extrisk_d0_extreme_and_moderate_noise.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))

@@

#------------- for extreme and moderate tail dep. noise : local dispersal summary fig. -------------------
pdf("./Results/allmodel_ext_risk_local_disp_extreme_and_moderate_noise.pdf",height=12,width=9)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.6,y=1.3, c("extreme LT","moderate LT","moderate RT","extreme RT"), lty=c(1,1,1,1), pch=c(1,1,1.1), 
       col=c('red', 'orange','skyblue','blue'), horiz=F, bty='n', cex=1.6, adj=0, x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-9, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-11, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist,noisetype = "both")

@@

pdf("./Results/allmodel_ext_risk_global_disp_extreme_and_moderate_noise.pdf",height=12,width=9)

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.6,y=1.3, c("extreme LT","moderate LT","moderate RT","extreme RT"), lty=c(1,1,1,1), pch=c(1,1,1.1), 
       col=c('red', 'orange','skyblue','blue'), horiz=F, bty='n', cex=1.6, adj=0, x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-9, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-11, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist, noisetype = "both")

@@

<!--FIG:  age structure model results for moderate tail dep. (C, SC)
\begin{figure}[!h]
\begin{center}
\textbf{ \hspace{0.5 cm} (A) \hspace{4.4 cm} (B)} \\
\vspace{-0.2 cm}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_linear.pdf}
\includegraphics[width=5 cm]{./Results/age_str_results/extrisk_age_str_C_SC_nonlinear_omg_100.pdf}
\caption[Extinction risk from single patch age structured models with time when vital rates have either left (C) or right tail (SC) association.]{Extinction risk (shading represents 95\% confidence interval) from single patch age structured models with time for 10000 simulations. Fecundity of adults and survival of eggs have moderate tail association in either left or right tail in their corresponding copula structure. Moderate left tail association (or right tail association) was generated by a bivariate Clayton (or Survival Clayton) copula with Kendall correlation coefficient = 0.6, $(A)$ for linear model ($\Omega = \infty$) and for $(B)$ non-linear model ($\Omega = 100$).\label{fig_extrisk_agestr_mtd}}
\end{center}
\end{figure}-->

<!--FIG:  summary: all nonlinear model results for global dispersion: extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extreme_and_moderate_noise.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{Analogous figure as of Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text but for global dispersal between metapopulation patches.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--FIG: Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme extreme tail dependent noises for 10000 simulations. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}
